\vspace{-0.5cm}The X-shooter GTO sample of GRB afterglow and host Galaxy spectra

### 2016-09-25 document/XSGRB_sample.tex

@@

	\subsection{GRB130606A (z = 5.913)}
	The data presented here also formed the basis of GCN \#
	14816\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/14816.gcn3}} and is published
	in \citet{Hartoog2015}. The observations consists of three 2x600sec visits
	starting 7.1 hr after the burst at fairly high airmass. We detect absorption
	features from a wide range of ions at $z=5.913$ as well as intervening
	absorption at $z=2.313, 2.521, 3.415, 4.6448, 4.6468, 4 and 4.6495$.

>>>>

	\subsection{GRB100728B (z=2.106)}
	The data presented here also formed the basis of GCN \#
	11317\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/11317.gcn3}}. The spectrum
	has not otherwise been published previously. Starting 22 hours after the burst
	trigger, 7.2 ks of observations reveals a faint afterglow continuum with \lya-
	and \mgii-absorption at $z=2.106$. Due to a malfunctioning ADC, the sensitivity
	of X-shooter is depressed with respect to normal operations, resulting in a
	poorer throughout. Additionally, the position of the trace on the slit moves
	due to atmospheric differential refraction.

@@

	\subsection{GRB130606A (z = 5.913)}
	The data presented here also formed the basis of GCN \#
	14816\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/14816.gcn3}} and is published
	in \citet{Hartoog2015}. The observations consists of three 2x600sec visits
	starting 7.1 hr after the burst at fairly high airmass. We detect absorption
	features from a wide range of ions at $z=5.913$ as well as intervening
	absorption at $z=2.3103, 2.5207, 3.4515, 4.4660, 4.5309, 4.5427, 4.6497 $ and $
	4.7244$.
